---
title: "Beta Streamflow Duration Assessment for the Western Mountains"
subtitle: "SDAM Version 1.0"
revision: "SDAM revision date: October 6, 2021" 
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output: pdf_document
always_allow_html: yes
params:
  a: NA
  b: NA
  c: NA
  d: NA
  e: NA
  f: NA
  g: NA
  h: NA
  i: NA
  j: NA
  k: NA
  l: NA
  m: NA
  n: NA
  o: NA
  p: NA
  r: NA
  s: NA
  t: NA
  u: NA
  v: NA
  w: NA
  aa: NA
  ab: NA
  ac: NA
  ad: NA
  ae: NA
  af: NA
  ag: NA
  ah: NA
  ai: NA
  aj: NA
  ak: NA
  al: NA
  am: NA
  an: NA
  ao: NA
  ap: NA
  aq: NA
  ar: NA
  as: NA
  at: NA
  av: NA
  ba: NA
  bb: NA
  bc: NA
  bd: NA
  be: NA
  bf: NA
  bg: NA
  bh: NA
  bi: NA
  bl: NA
  bm: NA
  bn: NA
  bo: NA
  tbl: NA
  fff: NA
  aqua_inv: NA
  may_flies: NA 
  indicator_taxa: NA 
  indicator_families: NA 
  f6: NA 
  f6_cap: NA 
  f7: NA 
  f7_cap: NA
  f8: NA 
  f8_cap: NA 
  notes_aquainv: NA 
  algae_streambed: NA 
  notes_algaecover: NA 
  f9: NA 
  f9_cap: NA 
  f10: NA 
  f10_cap: NA 
  f11: NA 
  f11_cap: NA
  fish_abundance: NA 
  fish_abundance_checkbox: NA 
  notes_fish_abundance: NA 
  f12: NA 
  f12_cap: NA
  f13: NA 
  f13_cap: NA 
  f14: NA 
  f14_cap: NA 
  vegetation_score: NA 
  notes_differences_vegetation: NA 
  f15: NA 
  f15_cap: NA 
  f16: NA 
  f16_cap: NA 
  f17: NA
  f17_cap: NA
  sinuosity: NA 
  notes_sinuosity: NA 
  f18: NA 
  f18_cap: NA 
  f19: NA 
  f19_cap: NA 
  f20: NA 
  f20_cap: NA 
  notes_supplemental_information: NA 
  f21: NA 
  f21_cap: NA 
  f22: NA 
  f22_cap: NA 
  f23: NA 
  f23_cap: NA 
  snow_or_no: NA 
  snow_persistence: NA 
  oct_precip: NA 
  may_precip: NA
  mean_temp: NA 
  modelused: NA
  class_wm: NA
  class_wm_msg: NA
  bankwidth: NA
  
---


```{r, setup, include=FALSE}
library(knitr)
# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

# Removing all "#" from appearing in the final knit document.
knitr::opts_chunk$set(comment = NA)

# Make error messages more descriptive
options(tinytex.verbose = TRUE)

opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

***

## Classification:

```{r}
cat(params$class_wm)
cat(paste0(glue::glue("Note: {params$class_wm_msg}")))
```

***

## General Site Information

Project name or number: `r params$a`

Site code or identifier: `r params$c`

Assessor(s): `r params$b`

Waterway name: `r params$d`

Visit date: `r params$e`

Current weather conditions: `r params$bm`

Notes on current or recent weather conditions:
```{r}
cat(params$j)
```

Location: `r paste0(params$g," N, ", params$h, " E")`

Surrounding land use within 100 m: `r params$l`

Description of reach boundaries: `r params$f`

Assessment reach length (m): `r if (!is.na(params$fff)){params$fff}`

Disturbed or difficult conditions:
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
cat(params$bn)
```

Notes on disturbances or difficult site conditions:
```{r}
cat(params$k)
```

## Observed hydrology:

Percent of reach with surface flow: `r params$m`

Percent of reach with surface and sub-surface flows: `r params$n`

Number of isolated pools: `r params$o`

Notes on observed hydrology: `r params$r`

***
## Site Photos

Top of reach looking downstream:
```{r, out.width = '50%', out.height= '50%', out.extra='angle=0', fig.align='center'}
if (!identical(params[["v"]], character(0))){ 
  knitr::include_graphics(params[["v"]])
}
```

Middle of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["u"]], character(0))){ 
  knitr::include_graphics(params[["u"]])
}

```

Middle of reach looking downstream:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["t"]], character(0))){ 
  knitr::include_graphics(params[["t"]])
}
```

Bottom of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["s"]], character(0))){ 
  knitr::include_graphics(params[["s"]])
}

```

## Site Sketch

```{r, out.width='50%', fig.align='center'}
if (!identical(params[["w"]], character(0))){ 
  knitr::include_graphics(params[["w"]])
}

```

***
## Indicators

Indicators used to classify the assessment reach are indicated with an asterisk.

## Climatic indicators

<!-- Snow persistence: -->
```{r}
cat(params$snow_persistence)
cat(paste0("The site is ",params$snow_or_no))
```

<!-- May precipitation (mm): -->
```{r}
if (!is.null(params$modelused) ) {
  cat(params$may_precip)
} else {
  cat("Data was not provided")
}
```
<!-- ```{r, out.width='50%', fig.align='center'} -->
<!-- knitr::include_graphics(params[["al"]]) -->
<!-- ``` -->

<!-- ```{r, out.width='50%', fig.align='center'} -->
<!-- knitr::include_graphics(params[["am"]]) -->
<!-- ``` -->

<!-- October precipitation (mm):  -->
```{r}
if (!is.null(params$oct_precip)) {
  cat(params$oct_precip)
} else {
  cat("Data was not provided")
}
```

<!-- Mean annual maximum temperature (Deg C):  -->
```{r}
if (!is.null(params$mean_temp)) {
  cat(params$mean_temp)
} else {
  cat("Data was not provided")
}
```

***
## Biological indicators

### Aquatic Invertebrates

Total abundance of aquatic macroinvertebrates: `r if (!is.null(params$aqua_inv)) {params$aqua_inv}`

Total abundance of mayflies: `r if (!is.null(params$may_flies)) {params$may_flies}`

Total abundance of perennial indicator families of aquatic macroinvertebrates: `r if (!is.null(params$indicator_families)) {params$indicator_families}`

Total number of perennial indicator families of aquatic macroinvertebrates: `r if (!is.null(params$indicator_taxa)) {params$indicator_taxa}`

Aquatic invertebrate photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6"]], character(0))){ 
  knitr::include_graphics(params[["f6"]])
}
  
```


```{r}

if (!identical(params[["f6"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7"]], character(0))){ 
  knitr::include_graphics(params[["f7"]])
}
  
```

```{r}
if (!identical(params[["f7"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8"]], character(0))){ 
  knitr::include_graphics(params[["f8"]])
}

```

```{r}
if (!identical(params[["f8"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_cap, perl = TRUE)))
}
```


Notes on aquatic invertebrates:

```{r}
cat(params$notes_aquainv)
```

***

### Algal Cover

Algal cover on the stream-bed: `r params$algae_streambed`

```{r}

if (params$ak){
  deposit <- case_when(
    params$ak == TRUE ~ "All observed algae appear to be deposited from an upstream source.")
  cat(deposit)
}

```

Notes on algal cover:

```{r}
cat(params$notes_algaecover)
```

Algae photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}
  
if (!identical(params[["f9"]], character(0))){ 
  knitr::include_graphics(params[["f9"]])
}
```

```{r}
if (!identical(params[["f9"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f9_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f10"]], character(0))){ 
  knitr::include_graphics(params[["f10"]])
}
```

```{r}
if (!identical(params[["f10"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f10_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f11"]], character(0))){ 
  knitr::include_graphics(params[["f11"]])

}

```

```{r}
if (!identical(params[["f11"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f11_cap, perl = TRUE)))
}
```

***

### Fish

Fish abundance: `r params$fish_abundance`

```{r}
if (params$fish_abundance_checkbox){
  cat("All fish observed were mosquitofish.")
}
```


Notes about fish abundance:

```{r}
cat(params$notes_fish_abundance)
```

Fish photos and descriptions: 

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f12"]], character(0))){ 
  knitr::include_graphics(params[["f12"]])
}

```

```{r}
if (!identical(params[["f12"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f12_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f13"]], character(0))){ 
  knitr::include_graphics(params[["f13"]])
}
```

```{r}
if (!identical(params[["f13"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f13_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f14"]], character(0))){ 
  knitr::include_graphics(params[["f14"]])
}

```

```{r}
if (!identical(params[["f14"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f14_cap, perl = TRUE)))
}
```

***

### Differences in vegetation

Differences in vegetation score: `r if (!is.null(params$vegetation_score)){params$vegetation_score}`

Notes about differences in vegetation:

```{r}
cat(params$notes_differences_vegetation)
```


Differences in vegetation photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f15"]], character(0))){ 
  knitr::include_graphics(params[["f15"]])
}

```

```{r}
if (!identical(params[["f15"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f15_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f16"]], character(0))){ 
  knitr::include_graphics(params[["f16"]])
} 

```

```{r}
if (!identical(params[["f16"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f16_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f17"]], character(0))){ 
  knitr::include_graphics(params[["f17"]])
}

```

```{r}
if (!identical(params[["f17"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f17_cap, perl = TRUE)))
}
```


***

## Geomorphological indicators

### Bankfull channel width (m): `r params$bankwidth`

### Sinuosity

Sinuosity score: `r if (!is.null(params$vegetation_score)){params$sinuosity}`

Notes about sinuosity:

```{r}
cat(params$notes_sinuosity)
```

Sinuosity photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f18"]], character(0))){ 
    knitr::include_graphics(params[["f18"]])
}

```

```{r}
if (!identical(params[["f18"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f18_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f19"]], character(0))){ 
    knitr::include_graphics(params[["f19"]])
}

```

```{r}
if (!identical(params[["f19"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f19_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f20"]], character(0))){ 
    knitr::include_graphics(params[["f20"]])
} 

```

```{r}
if (!identical(params[["f20"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f20_cap, perl = TRUE)))
}
```

***

## Supplemental Information

Additional notes about the assessment:

```{r}
cat(params$notes_supplemental_information)
```

Supplemental information photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f21"]], character(0))){ 
    knitr::include_graphics(params[["f21"]])
}

```

```{r}
if (!identical(params[["f21"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f21_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f22"]], character(0))){ 
    knitr::include_graphics(params[["f22"]])
}
```

```{r}
if (!identical(params[["f22"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f22_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f23"]], character(0))){ 
    knitr::include_graphics(params[["f23"]])
}

```

```{r}
if (!identical(params[["f23"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f23_cap, perl = TRUE)))
}
```

**End of Report**
